\Huge Handwritten digit recognition

### 2017-02-08 doc/Paper.tex
Addproblem statement

\newpage
\TODO{introduction?}

\section{Problem statement}
\label{sec:problem}
Given a picture of a handwritten digit, label it accordingly 0 - 9.
\TODO{more here}

@@

We use a back-propagation neural network:
\begin{align*}
W^{(k)} &= W^{(k-1)} + \alpha \nabla_W^{(k-1)} \\ 
b^{(k)} &= b^{(k-1)} + \alpha \nabla_b^{(k-1)}
\end{align*}
Where $W$ is the weights matrix, $10 \times 784$ -- the number of classes( one for each digit) and the dimension of an image ($28 \times 28$). $b$ is the bias vector, $1 \times 10$, corresponding to the free element. $W^{(k)}$ denotes the weights at step $k$. $\nabla$ represents the update which must produce to improve prediction.
\\

The activation function is softmax:
$$f(x_i)=\frac{exp(x_i)}{\sum_j exp(x_j)}$$
Where $exp(x)$ represents $e^x$, Euler's constant. It \textit{normalizes} the vector, causing the greatest elements to have logarithmic relative value.
\\

@@

\paragraph{Training} We employ gradient-descent on mini-batches. Early-stopping prevents the model from further learning when performance on the validation split starts decreasing. Random sampling averts cycles when iterating through the dataset.

\paragraph{Prediction}
\TODO{explain prediction?}

>>>>

\newpage
\section{Introduction}
\TODO{more here}

\section{Problem statement}
\label{sec:problem}
Pentru o retea neurala care foloseste un algoritm de antrenare bazat pe metoda gradientului descendent si dispune de o cantitate mare de date de antrenare timpul ca reteaua sa ajunga la rezultate satisfacatoare poate dura chiar si zile pe o implementare secventiala
Ne propunem sa elaboram o implementare paralela a metodei gradientului descendent. Vom folosi pentru validarea implementarii o problema celebra in computer vision, cea a detectarii cifrelor scrise de mana.

For a neural network witch use for training the gradient descendent algorithm and dispose a large amount of training data, the time to reach convergence it can take days in a sequentially implementation.
We purpose to elaborate a parallel implementation of gradient descendent, and for validate that we use a common problem in computer vision: given a picture of a handwritten digit, label it accordingly 0 - 9.

@@

We use a feed-forward neural network with an one fully connected layer, which predict the digit that has been in input image.
For an image $x$, initialy $28 \times 28$, we flatten this array into a vector of $784 = 28 \times 28$.

\begin{align}
y = softmax(Wx + b) \\
image\_label &= argmax(y)
\end{align}

In $(1)$, $W$ is the weights matrix, $10 \times 784$ -- the number of classes(one for each digit) and the dimension of an image ($784$). $b$ is the bias vector, $1 \times 10$, corresponding to the free element.
\\

The activation function output a vector of probabilities:
$$softmax(x_i)=\frac{exp(x_i)}{\sum_j exp(x_j)}$$
Where $exp(x)$ represents $e^x$, Euler's constant. It \textit{normalizes} the vector, causing the greatest elements to have logarithmic relative value.
\\

$(2)$ With $y$ vector of probabilities, $argmax$ take the index of the maximum value and results the prediction label.

@@

\paragraph{Training} We employ gradient-descent on mini-batches. 
\begin{align*}
W^{(k)} &= W^{(k-1)} + \alpha \nabla_W^{(k-1)} \\ 
b^{(k)} &= b^{(k-1)} + \alpha \nabla_b^{(k-1)}
\end{align*}
Where $W$ is the weights matrix, $10 \times 784$ -- the number of classes( one for each digit) and the dimension of an image ($28 \times 28$). $b$ is the bias vector, $1 \times 10$, corresponding to the free element. $W^{(k)}$ denotes the weights at step $k$. $\nabla$ represents the update which must produce to improve prediction.
\\
Early-stopping prevents the model from further learning when performance on the validation split starts decreasing. Random sampling averts cycles when iterating through the dataset.
